\documentclass[letterpaper,10pt]{article}

\usepackage[english]{babel}
\usepackage{catchfile}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[empty]{fullpage}
\usepackage[top=0.5in,bottom=0.5in,left=0.5in,right=0.5in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage[default]{sourcesanspro}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{verbatim}
\usepackage{xstring}

\input{glyphtounicode}

% Ensures PDF is machine-readable and parsable for ATS
\pdfgentounicode=1
% omits PDF metadata for reproducible builds
\pdfinfoomitdate=1
\pdftrailerid{}

% parses .git metadata and populates PDF info
\CatchFileDef{\headfull}{.git/HEAD}{}
\StrGobbleRight{\headfull}{1}[\head]
\StrBehind[2]{\head}{/}[\branch]
\IfFileExists{.git/refs/heads/\branch}{
  \CatchFileDef{\commit}{.git/refs/heads/\branch}{}
}{
  % assuming detached HEAD
  \renewcommand{\branch}{}
  \newcommand{\commit}{\headfull}
}

\AfterPreamble{
  \hypersetup{
    pdfauthor={Johnny Tran},
    pdfinfo={
      GitBranch={\branch},
      GitCommit={\commit}
    },
    pdftitle={Resume}
  }
}

\titleformat{\section}{\vspace{-12pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule{}\vspace{-5pt}]

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% Bigger than \huge. skip should be 1.2 times size
\newcommand\Yuge{\fontsize{24}{30}\selectfont}

\newcommand{\subsectionStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\subsectionEnd}{\end{itemize}}

\newcommand{\experienceHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} (\textit{\small#3 --- \textit{\small #4}})& #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\eduHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}
\newcommand{\experienceStart}{\begin{itemize}[leftmargin=16pt, rightmargin=8pt]}
\newcommand{\experienceEnd}{\end{itemize}\vspace{-7pt}}
\newcommand{\experience}[1]{\item\small{{#1 \vspace{-0.5pt}}}}
\newcommand{\skills}[2]{\item\small{{\textbf{#1}: #2\vspace{-6pt}}}}

\raggedright{}

\begin{document}

\begin{center}
    \textbf{\Yuge{Johnny Tran}} \\ \vspace{4pt}
    \href{mailto:jtrandev@gmail.com}{jtrandev@gmail.com} $|$
    (619) 940--4271 $|$
    San Diego, CA 92122 $|$
    \href{https://linkedin.com/in/johnnytran0}{linkedin.com/in/johnnytran0} $|$
    \href{https://github.com/johnnytran0}{github.com/johnnytran0}
\end{center}

\section{Experience}
\subsectionStart{}
  \experienceHeading{Software Engineering Manager}
    {Dec. 2021 --- Sept. 2024}
    {UKG}
    {Hybrid Remote}
  \experienceStart{}
    \experience{
      Led a high-performing distributed team of 7+ engineers to release quarterly roadmap product  deliverables and maintain enterprise SaaS systems for  Conversations \& Feedback modules in the UKG Pro Performance \& Coaching product suite.
    }
    \experience{
      Facilitated collaboration leveraging SAFe Agile methodologies to align product vision across cross-functional teams, including Architecture, Engineering, Operations, Product, Program Management, Quality, and key internal stakeholders, planned product roadmap amid ambiguities, and overcame project challenges to meet critical milestones.
    }
    \experience{
      Oversaw the planning and execution of all facets of the software development lifecycle (SDLC), collaborated hands-on with teammates during architectural debates, design discussions, code reviews, and quality assurance, assessed tradeoffs of major technical decisions, and enforced software development best practices to ensure high-quality code, implemented using Angular, GraphQL, Docker, Java, Javalin, Kafka, Kotlin, Kubernetes, Looker, MongoDB, MySQL, and Spring Boot.
    }
    \experience{
      Spearheaded long-term engineering initiatives to transition microservices architecture from Axon Framework CQRS to a scalable Outbox pattern implemented using internal Kotlin SDK, reducing system complexity and service overhead by 25\%.
    }
    \experience{
      Triaged production defects, managed incident resolution with SREs, performed root cause analysis, and actioned monitoring changes in DataDog and Grafana, reducing mean response time for major PagerDuty incidents to less than 30 minutes.
    }
    \experience{
      Hired, mentored, and coached engineers at all levels, conducted regular 1:1 meetings, provided actionable performance feedback, aligned role-specific goals with company OKRs, supported team members' career development by growing technical skills and leadership capabilities, and fostered a team culture of continuous improvement.
    }
  \experienceEnd{}

  \experienceHeading{Principal Software Engineer}
    {June 2021 --- Dec 2021}
    {UKG}
    {Remote}
  \experienceStart{}
    \experience{
      Designed and implemented infrastructure as code tooling to automate, manage, and provision UKG Pro Coaching \& Development services using Kubernetes and Google Cloud Platform, achieving production-readiness of the first US region.
    }
    \experience{
      Accelerated product release capabilities by establishing DevOps guardrails for continuous delivery, switched CI/CD branching strategy from Gitflow to trunk-based development, adopted feature flagging via LaunchDarkly SDK, improved change lead time from weeks to days, and increased deployment frequency from quarterly to biweekly.
    }
  \experienceEnd{}

  \experienceHeading{Staff Software Engineer}
    {Jan. 2021 --- June 2021}
    {UKG}
    {Remote}
  \experienceStart{}
    \experience{
      Drove initiatives to improve developer knowledge base quality and build a self-service documentation portal as the team scaled from 10 to 25+ distributed engineers spanning multiple time zones, improved time to productivity for onboarding new hires to less than 4 weeks by consolidating technical content on Backstage, Confluence, LucidCharts, and Microsoft SharePoint.
    }
    \experience{
      Coordinated Engineering, Product, Operations, and Quality leads to plan, prioritize, and task Jira Epics to meet functional and non-functional requirements, communicated estimates, issues, and dependencies between stakeholder teams, resulting in a 50\% reduction in integration change failures over two quarters.
    }
  \experienceEnd{}

  \experienceHeading{Lead Software Engineer}
    {Dec. 2018 --- Jan. 2021}
    {UKG}
    {Remote}
  \experienceStart{}
    \experience{
      Led cross-functional distributed engineering teams of 7+ using Kanban methodology to decouple Continuous Feedback features from Employee Voice Python2 monolith into microservices platform, successfully orchestrated cut-over migration for over 100 tenants, implemented using Angular, Axon, Cloud Foundry, GraphQL, Java, MongoDB, RabbitMQ, and Spring Boot.
    }
  \experienceEnd{}

  \experienceHeading{Senior Software Engineer}
    {Sept. 2016 --- Dec. 2018}
    {Ultimate Software}
    {Remote}
  \experienceStart{}
    \experience{
      Collaborated with Product, Data Scientists, and Data Platform teams to launch an employee retention risk dashboard and ML predictive model trained on UltiPro employment data using Apache Hadoop, NumPy, Pandas, Python, and scikit-learn.
    }
    \experience{
      Engaged with Product and Engineering stakeholders using Domain-Driven Design approaches to define bounded contexts and aggregates for new UltiPro Payroll and People features, applied 12-Factor App principles to implement 10+ microservices using CQRS and event-sourcing patterns, and reduced system complexity by 30\% through business-aligned domain modeling.
    }
  \experienceEnd{}

  \experienceHeading{Software Engineer}
    {April 2014 --- Sept. 2016}
    {Teradata}
    {Rancho Bernardo, CA}
  \experienceStart{}
    \experience{
      Implemented Teradata Viewpoint portlets using Scrum methodology, built responsive web/mobile UIs with Backbone.js and Spring MVC, and designed RESTful API controllers for monitoring system health and query log of Teradata Database systems.
    }
  \experienceEnd{}
\subsectionEnd{}

\section{Education}
\subsectionStart{}
  \eduHeading{University of California, San Diego}
    {San Diego, CA}
    {Computer Engineering, Bachelor of Science}
    {2009 --- 2014}
\subsectionEnd{}

\section{Technical Skills}
\begin{itemize}[leftmargin=6pt, rightmargin=8pt, label={}]
  \skills{Programming Languages}
    {Java, JavaScript/TypeScript, Kotlin, Python}
  \skills{Databases}
    {Elasticsearch, InfluxDB, MongoDB, MySQL, PostgreSQL, Redis}
  \skills{Technologies}
    {Angular, Ansible, Apache Kafka, Bash, Bitbucket, Cloud Foundry, Concourse, Confluence, Cypress, DataDog, Docker, Gatling, Git, GitHub, GitHub Actions, Google Cloud Platform, Gradle, Grafana, GraphQL, HTML/CSS,  Jasmine, Javalin, JetBrains IDEs, Jira, JMeter, JUnit, Kibana, Kubernetes (k8s), LaTeX, LaunchDarkly, Linux/Unix, Looker, LucidCharts, Markdown, Maven, Microsoft 365, Node.js, OAuth2, OIDC, PagerDuty, PlantUML, Postman, Prometheus, RabbitMQ, Slack, SonarQube, Spring Boot, Spring Framework, TeamCity, TestRail}
\end{itemize}

\end{document}
